{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-28 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

                Let $f: \RR^n \rightarrow\overline \RR$ be an l.s.c proper function. 

@@

                If $q = 0$, $f$ is convex or strongly convex. 
                If $f$ is weakly convex, then $f + 1/2\Vert \cdot\Vert^2$ is convex and, it has $\dom f$ convex, and locally Lipschitz continuous on $\reli \dom f$. 

@@

                Optimizing $x\mapsto x - x^2(1_g - L)/2$ yields $x = (q_g - L)^{-1}$ so $\beta = q_g - L$ gives the most amount of descent. 
                Consider any $\beta \ge (q_g - L)$: 

@@

                    F(x) - F(\bar x) + \frac{1}{2\beta}\Vert\mathcal G_{1/\beta}(x) \Vert^2. 

@@

            Suppose that the sequences $(y_{k + 1}, v_k, x_k)_{k \ge 0}$ and $(\hat y_k, \tilde x_k)_{k \ge 0}$, $(\alpha_k)_{k \ge 0}$ satisfy Definition \ref{alg:nes-mono}. 

>>>>

                Let $F: \RR^n \rightarrow\overline \RR$ be an l.s.c proper function. 

@@

                If $q = 0$, $F$ is convex.
                If $F$ is weakly convex, then $F + q/2\Vert \cdot\Vert^2$ is convex and, it has $\dom F$ convex, and locally Lipschitz continuous on $\reli \dom F$. 

@@

                % Optimizing $x\mapsto x - x^2(q_g + L)/2$ yields $x = (q_g + L)^{-1}$ so $\beta = q_g - L$ gives the most amount of descent. 
                Consider any $\beta \ge (q_g + L)$: 

@@

                    F(x) - F(\bar x) - \frac{1}{2\beta}\Vert\mathcal G_{1/\beta}(x) \Vert^2. 

@@

            Suppose that the sequences $(y_{k + 1}, v_k, x_k)_{k \ge 0}$ and $(\hat y_k, \tilde x_k)_{k \ge 0}$, $(\alpha_k)_{k \ge 0}$ satisfy Definition \ref{def:nes-monotone-scheme}. 
